Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
Minor fixes, typos, etc
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1619 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\documentclass[11pt]{article}
\usepackage{acl2010}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage[colorlinks]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{xspace}

@@

The toolkit has then been used by the authors and several
other groups in their daily research, and thus much progress has
been made to the first version. 
In this paper, we will describe the main new functions we have added into the 
toolkit, which include: 
\begin{itemize}
\item
supporting for the syntax-augmented machine translation (SAMT) grammar \cite{samt2006},
\item
supporting mannual constraints in the input to constrain the decoding \cite{PBML-2010-Josua-transliteration},  
\item
lattice parsing for dealing with input uncertainty \cite{dyer-muresan-resnik:2008:ACLMain},
\item
semiring parsing for unified dynamic programming \cite{li-eisner:2009:EMNLP} , 
\item
variational decoding for approximating the intractable MAP decoding \cite{variational-decoding-acl09},
\item
hypergraph-based discriminative training for better feature engineering \cite{zhifei-forest-reranking-galebook}, 
\item
visualization of the derivation trees and hypergraphs \cite{PBML-2010-Josua-visualization}, 
\item
and a unified pipeline for MT experiments \cite{Schwartz-wmt10-pipline}.
\end{itemize}
Below we give a short description for each of the new functions added.

>>>>

\documentclass[11pt]{article}
\usepackage{acl2010}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
%\usepackage[colorlinks]{hyperref}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{xspace}

@@

The toolkit has been used by the authors and several
other groups in their daily research, and thus much progress has
been made to the first version. 
In this paper, we describe the main new functions we have added into the 
toolkit, which include: 
\begin{itemize}
\item
supporting for syntax-augmented machine translation (SAMT) grammar \cite{samt2006},
\item
supporting manual constraints in the input to constrain the decoding \cite{PBML-2010-Josua-transliteration},  
\item
lattice parsing for dealing with input uncertainty \cite{dyer-muresan-resnik:2008:ACLMain},
\item
semiring parsing for unified dynamic programming \cite{li-eisner:2009:EMNLP} , 
\item
variational decoding for approximating the intractable MAP decoding \cite{variational-decoding-acl09},
\item
hypergraph-based discriminative training for better feature engineering \cite{zhifei-forest-reranking-galebook}, 
\item
visualization of the derivation trees and hypergraphs \cite{PBML-2010-Josua-visualization}, 
\item
and a unified framework for designing and running reproducible machine translation experiments \cite{Schwartz-wmt10-pipline}.
\end{itemize}
Below we give a short description for each of the new functions added.
